Data preparation for employee category analysis

### 2023-04-20 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Testing another approach to correlations between days

```{r}
cohort_panel %>% 
  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
  mutate(ind = 1) %>% 
  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
  clean_names() %>% 
  select(person_id,date,date_day_of_week,teleworking) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  mutate(
    date_week_start = floor_date(date,unit = "week")) %>% 
  select(-date) %>% 
  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  group_by(person_id) %>%
  # filter(person_id == "10070")
  summarise(cor = cor(Fri,Wed,method = "kendall", use = "complete.obs"))
```

>>>>

```{r correlation remote only}
cohort_panel %>% 
  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
  mutate(ind = 1) %>% 
  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
  clean_names() %>% 
  select(person_id,date,date_day_of_week,teleworking) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  mutate(
    date_week_start = floor_date(date,unit = "week")) %>% 
  select(-date) %>% 
  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  group_by(person_id) %>%
  # filter(person_id == "10070")
  summarise(cor = cor(Fri,Wed,method = "kendall", use = "complete.obs"))
```

```{r correlation ordered status}
cohort_panel %>% 
  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
  mutate(
    daily_status_imputed = fct_lump_prop(daily_status_imputed, prop = .1),
    daily_status_imputed = fct_infreq(daily_status_imputed),
    daily_status_imputed = factor(daily_status_imputed, ordered = TRUE)
  )  %>% 
  mutate(
    date_week_start = floor_date(date,unit = "week")) %>% 
  select(-date) %>% 
  pivot_wider(values_from = daily_status_imputed,names_from = date_day_of_week) %>% 
  mutate(
    across(
      .cols = where(is.factor),
      .fns = ~replace_na(.,"Other")
    )
  ) %>% 
  group_by(person_id) %>%
  # filter(person_id == "10070")
  summarise(cor = cor(as.numeric(Fri),as.numeric(Wed),method = "spearman", use = "complete.obs"))
# %>% 
  count(daily_status_imputed)
```
